Density dependence

### 2020-10-07 analysis/paper/appendix_density_dependence.Rmd
extracted marginal effects for crossbasis smooths function to .R file.  Removed unused functions and dependencies

```{r setup, include=FALSE}
knitr::opts_chunk$set(inclue = FALSE)
library(tidyverse)
library(here)
library(conflicted)
library(lme4)
library(bbmle)
library(car)
library(broom)
library(broom.mixed)
# library(patchwork)
# library(performance)
library(dlnm)
library(mgcv)
# library(visibly) # better diagnostic visulazations.  one of several packages for this.
source(here("R", "utils.R"))

@@

-   Remove unecessary dependencies

-   Move functions to .R file

-   Rearrange analysis with GAM first

@@

```{r}
pred_growth <- pred_cb(Q, L, g_growth)
```

```{r}
#TODO:
# - marginal_cb() function should add the min_dist column.
# - plot_marginal_cb() function should do ggplot stuff and include a too.far argument
# - All this moved into a .R file that is source()d
dat <-
  ha %>%
  select(shts_0.5_1:shts_4.5_5) %>% 
  pivot_longer(everything(),
               names_prefix = "shts_",
               names_sep = "_",
               names_to = c("inner", "outer"),
               names_transform = list(inner = as.numeric, outer = as.numeric),
               values_to = "x") %>% 
  mutate(lag = (inner + outer) / 2)

which.too.far <- function(grid, data, x, y, dist = 0.1) { 
  x <- enquo(x)
  y <- enquo(y)
  # x <- quo(x)
  # y <- quo(lag)

  grid1 <-
    grid %>% 
    mutate(min_g_x = min(!!x, na.rm = TRUE),
           min_g_y = min(!!y, na.rm = TRUE),
           g_x = !!x - min_g_x,
           g_y = !!y - min_g_y) %>% 
    mutate(max_g_x = max(g_x, na.rm = TRUE),
           max_g_y = max(g_y, na.rm = TRUE),
           g_x = g_x / max_g_x,
           g_y = g_y / max_g_y)

  data1 <-
    data %>% 
    mutate(d_x = (!!x - first(grid1$min_g_x)) / first(grid1$max_g_x),
           d_y = (!!y - first(grid1$min_g_y)) / first(grid1$max_g_y))

  if (dist < 0)
    stop("supplied dist negative")

  #where dat is a 2-column matrix of x and y coords of the true data used to build the model
  min_dist <- function(g_x, g_y, dat) {
    dat[,1] <- dat[,1] - g_x
    dat[,2] <- dat[,2] - g_y
    min(
      sqrt(
        (dat[,1]^2 + dat[,2]^2)
      ), na.rm = TRUE
    )
  }
  o <- 
    grid1 %>%
    rowwise() %>%
    mutate(min_dist = min_dist(g_x, g_y, cbind(data1$d_x, data1$d_y)),
           too.far = min_dist > dist) %>% 
    select(-g_x, -g_y, -max_g_x, -max_g_y, -min_g_x, -min_g_y)
  return(o)
}

pred_growth <- which.too.far(pred_growth, dat, x = x, y = lag)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(inclue = FALSE)
library(tidyverse)
library(here)
library(conflicted)
library(bbmle)
library(dlnm)
library(mgcv)

# library(lme4)

# library(car)
# library(broom)
# library(broom.mixed)

source(here("R", "crossbasis.R"))

@@

-   Remove unnecessary dependencies

-   Rearrange analysis with GAM first (i.e. finish adding `glmer()` code)

@@

```{r}
pred_growth <- cb_margeff(Q, L, g_growth)
```
